The limits of self commitment and private paternalism \thanks{}

### 2020-05-30 main.tex
update before restructure

@@

\title{Frequent Payment \thanks{}}
\author{Joyce Sadka \and Enrique Seira  }
\date{This draft:  \today \\[2 cm]}

@@

\maketitle
\begin{abstract}
XXX 
\end{abstract}

\textbf{Keywords: } XXX.

\textbf{XXX} XXX

@@

@@

\section{Conclusion}

>>>>

\usepackage{lmodern} 
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\wh}{\widehat}
\onehalfspacing

@@

\title{The limits of self commitment and private paternalism \thanks{}}
\author{Joyce Sadka \and Enrique Seira \and Isaac Meza  \thanks{Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
\date{This draft:  \today \\[2 cm]}

@@

\maketitle
\begin{abstract}

%Many firms provide commitment devices that restrict individuals' choice, but shroud this. Shrouding suggests low demand for commitment. We show that private paternalism is beneficial in the pawnbroker context we study.

We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context. We show that forcing people into commitment contracts with financial penalties for not paying on time decreases their (fee-including) financial cost by \hlgr{11\%}, increases the likelihood of recovering their pawn by \hlgr{23\%}, and increases the likelihood of repeat business by \hlgr{20\%}. While virtually all clients would reduce their financing cost with the commitment contract, we show that only 10\% choose it. Using salient personal promises instead of pecuniary penalties as commitment triples contract take-of, but has not effect on financial costs or pawn recovery.

%and one of the most understudied. In our context more than on half of borrowers default and lose their pawn and whatever they have paid towards recovering it. Compared to the status quo pay-at-anytime 3-month contracts, forcing borrowers to pay monthly and charge a penalty if they didn't --i.e. a commitment contract-- increased recovery of pawn by about 30\% and financial costs by 10\%. However when offered a choice between the two contracts only 10\% took the monthly payment one. A pecuniary commitment seems necessary. In an alternative arm, we made them promise to pay but removed the pecuniary penalty. This increased take up to 31\%, but had zero effect on financing cost or default. The forcing contract may be better than choice for naive present biased consumers.

\end{abstract}

\textbf{Keywords: } Private paternalism, choice, present bias, commitment, pawnshops.

\textbf{JEL codes:} XXX

@@

%NO MORAL HAZARD IN THE CONTRACT SINCE FULLY COLLATERALIZED
%DOUBLE FAILURE: DEMAND LOW, AND DOES NOT WORK BY PEOPLE WHO TAKE IT.
%PENALIZES THEM EVEN MORE ON SOMETHING THEY WERE ALREADY PENALIZED 
%PROPENSITY TO CHOSE.
%PULLING PUNISHMENT FORWARD --CHARGING RIGHT WHEN I MESS UP.
%MAYBE ONLY IMPATIENT AND NAIVE END IN PAWNSHOPS
%1) SELECT A RANDOM SAMPLE OF NEIGHBORHOODS, EXTERNAL VALIDITY, THE ONES THEY GO ARE NAIF AND
%HYPERBOLIC
%2) ASK TO CHOSE AMONG ALL CONTRACTS
%3) CLASSIFY SOPHISTICATION AT BASELINE
%4) HOW TO GET AT SHOCKS.  --BUT DOES NOT SQUARE WITH WHY CHARGING THEM FEES WORKE.
%do shocks vary across strata, predict shocks.
%DEEP BEHAVIORAL PAPER -- CAN WE REALLY PREDICT?

@@

\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers, students, borrowers overcome self-control problems. ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''. Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''. However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''. In this, he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them. The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.

This paper studies private paternalism in the context of pawnbroker borrowing and finds evidence for its benefits. Pawnshops offer secure loans using items of personal property as collateral. The items pawned are called pledges or pawns. Pawn loans are one of the oldest forms of borrowing, and although data on their market share is scarce, anecdotal evidence suggests they are very prevalent. To give an example, our partner pawnshop (henceforth Lender $P$) served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were approximately 2.3 million micro-finance clients in Mexico in 2009 in Mexico (\cite{Pedroza:2010}). We cannot be more precise on the number of total borrowers from Lender $P$ for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone. But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to. The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and are more likely to be present biased and naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients: \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}

Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. Conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment. In our survey 68\% report self-control problems in several domains.%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

Consistent with little client sophistication, Lender $P$ offers a very simple but highly collateralized contract. It only accepted gold jewelry as collateral and approves all gold pawns, giving in exchange in cash the equivalent of 70\% of the weighted gold value. The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest. The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties. However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this). All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch. The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry. Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers. %This lets us focus more cleanly on behavioral economics aspects.

To study the benefits of private paternalism, we implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying their monthly installment on time can actually decrease total fee-inclusive financing cost. Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice? Notice that any payment profile implemented in the commitment contract can be replicated under the status quo contract, but the later has more flexibility to respond to income shocks without incurring in fees. Third, what types of clients would demand these contracts that restrict choice? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{Status-quo group}). The second arm (\textit{Fee-forced group}) was assigned into a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by \hlgr{11\%} on average, while the likelihood of recovering their pawn increases by \hlgr{19\%}. This is robust to including  transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings. The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings. Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, we find that borrowers assigned to the forced fee-commitment contract are \hlgr{5pp} (\hlgr{20\%} of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.

%From this first comparison we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default actually helps borrowers. In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat costumers, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms. \cite{Laibson2018} conjectures that this exploitation may be limited if consumers use experienced utility to choose among firms or contracts.}

In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low. Only \hlgr{10\%} of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract. We had two assistants from the research team in each of the experiment's branches every day for all branch opening hours, material was developed to explain the differences among the two contracts, and subjects spelled back to assistants the loan differences. Furthermore take up is systematically predicted by baseline covarites\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.}, making it less likely that it is just random mistakes. Low demand for commitment is consistent with most of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could we welfare improving for the naive. We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery. These effects are zero throughout the quantile distribution.

 %Using boosting we can predict who takes up with 92\% accuracy. This fact shows that the choice among contracts is not purely random.

How much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \hlgr{\$300} pesos, close to 10\% of the average loan value. In particular \hlgr{95\%} of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hlgr{7\%} of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be welfare increasing for the overwhelming majority of clients.

Inspired by a significant lab experiment literature on the effects of promises on behavior, we also implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To do this we implemented two other treatment arms. A \textit{promise-forced} arm exactly analogous to our \textit{fee-forced arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise. Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise-forced} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the \textit{Promise-forced} contract is three times bigger than for the \textit{Fee-forced} contract, with \hlgr{31\%} take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view. Second, the \textit{Promise-forced} contract had zero effects on average and for an overwhelming fraction of the population on financing cost and pawn recovery. The same is true for the \textit{Promise-choice arm}. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior. Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.\footnote{The government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but they rely on group lending, and therefore social collateral is at stake.}

%\footnote{This is consistent with \cite{Belot2010}, who emphasize that elicited promised may have lower effects than voluntary ones.}
%\cite{Rabin2018} and \cite{Ted} show that naivete may lead to the choice of to little commitment. 
%Before discussing results, let us mention why these questions are relevant and how they relate to the literature. Most of microfinance involves frequent payments/meeting with the group --sometimes weekly-- even though this increases transaction costs. Several hypothesis have been postulated to explain this, from increased group's cohesion and monitoring, to forming personal payment habits or serving as a commitment device. Most of the literature (e.g. \cite{Pande}) find however null effects of increasing frequency on default, and therefore on payment habits, commitment, or peer pressure.

The paper is organized as follows. Section \ref{context} provides context and describes the data sources. Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms. Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice. Section \ref{promises} assesses if promises work in our context as commitment devices. Finally, Section \ref{conclusion} concludes.

\section{Context and Data} \label{context}

\subsection{The pawn lender and high default rates}

Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``energency'' loans. They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}). In spite of this, there are extremely few studies in the economics literature about it. Why people go, how much it costs, what different contracts can tell us about consumer biases. We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with \hl{several hundred} branches spanning multiple States in Mexico.

Lender $P$ was interested in understanding why half of their clients lost their pawn. It was concerned with high default rates for two reasons. The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece. We actually find that clients report a subjective value that is almost \hlgr{twice} the value of its gold content. Second, it thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again. They were interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract. Default is really  in this context  compared to many papers in the microfinance literature. \cite{Pande} study of the effect of payment frequency work in a context where the rate of default is close to 1\%. \cite{LittleAtAtime} has a baseline default of \hl{XX\%}.

One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for \hlgr{86\%} of them, but also because among that lose their pawn \hlgr{74\%} paid a positive amount towards its recovery. This can only be rationalized if they expected to recover their pawn.  Figure \ref{proxy_naive} focuses on those that ended up losing the pawn in our experiment and plots different measures of engagement with Lender $P$. Panel (c) shows total payments that went towards the loan. On average clients that lost their pawn paid \hlgr{34\%} of the value their loan. Panel (d) shows that while 40\% made zero payments, the rest made one or several payments. In fact, panel (b) shows that close to \hlgr{50\%} of clients extended the loan for another cycle and made payments in the second cycle.

\subsection{The status quo contract}

Their business model is very simple. They take gold jewelry as collateral in exchange for a fraction of money given instantly in cash. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller). The appraiser weights the gold piece and runs tests on its purity. Based on these he assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece instantly and in cash to the costumer. The costumer signs a 2-sheet contract with the main conditions of the contract at the branch and leaves with the cash.

Lender $P$ had only one type of contract. It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime and no penalty for pre-payment. If the client paid the principal plus the accumulated interest before those 105 days, the she received back her pawn, otherwise the pawnbroker kept the piece and any payments done. Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms. The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.

This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn. Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history. Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though \hlgr{90\%} of them have pawned before.

\section{Data and summary stats}

We worked in 6 branches of Lender $P$ of differing size and location, although for simplicity all of them in Mexico city. For these 6 branches we have two types of data, administrative data and survey data we collected ourselves for the experiment.

\subsection{Administrative Data}
The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece. In particular, the value of the piece as assessed by the appraiser, the amount of money lent (70\% of the value), and the date when it was pawned. As described below, for our experiment we also recorded the type of contract for that pawn. After the pawn happens, we follow each transaction related to that piece in the administrative data: when were payments made and for which amounts, whether there was default (i.e. the client lost her pawn), and whether any late-payment fees (active for only some experimental arms) were imposed. We have this information for all the pawns that occurred in our 6 branches between \hlgr{August 6th 2012 and August 13th 2013}, this includes all the pawns under our experiment but also those that happened \hlgr{1} month before it started and up to \hlgr{8} months after it ended. Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage. The black arrow represent the dates for which we have administrative data (before and after the experiment) while the light gray represents the duration of the experiment. The experiment comprises \hlgr{13,443} pawns, and our administrative data cover a total of \hlgr{26,181} pawns.

\subsection{Survey Data}

We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece. The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others. We were able to survey \hlgr{7,703} clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
\hlgr{The appendix transcribes the questionnaire in English and presents summary stats}. Survey response rate is 57\%, \hlgr{the Appendix Table} \ref{balance_response} shows that response is not related to admin data observables.

\subsection{Summary statistics}

Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm. Because treatment arms are described below, here we concentrate on the overall average. Panel A describes variables from the administrative data. It shows that the average loan size is \hlgr{\$1945} pesos (\hlgr{\$105} usd). The average number of pawns per day per branch is \hlgr{33}. Although not shown in the table, only \hlgr{40\%} of clients recover they pawn within \hlgr{230 days}. Even those that recover their pawn tend to pay ir back at the last moment, only \hlgr{20\%} pay before the \hlgr{90}th day.

Panel B reports stats from our survey data. We learn that \hlgr{73\%} of clients are women, with an average age of \hlgr{44} years; \hlgr{66\%} of them have completed high school or more, and \hlgr{90\%} have pawned before, so that our sample has mostly experienced borrowers. Finally the subjective probability of recovery is close to \hlgr{93\%} on average, which contrast with the \hlgr{44\%} recovery that happens in reality for the pawns \hlgr{in the control group}. Just by this measure borrowers seem to be highly overconfident on average. It turns out that the average subjective value they report for the pieces is  \hlgr{6292 pesos}, which is much larger than the average appraised gold value (\hlgr{3222 pesos}). This makes it inefficient for them to lose it.

Since the main treatment involves making them come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions around them. The average time they take to come to the branch is \hlgr{22 minutes}, and the amount of money they spend in transport to do that is \hlgr{11 pesos} \hlgr{(\$0.60 usd)}.  
The population we are working with is economically vulnerable in the sense that \hlgr{31\%} of them could not pay \hlgr{either} water, electricity \& gas or rent in the past \hlgr{6} months. They often receive negative income shocks: \hlgr{87\%} said they are pawning because of an emergency, and only \hlgr{13\%} stated it was to use in a \hlgr{`non-urgent expense'}.
%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),

\subsection{Financing cost and Default} \label{FC_def}

Our main dependent variables are loan default and financial cost incurred by the borrower. Default is defined as losing the pawn. We observe directly when the piece gets appropriated by Lender $P$ and goes on sale.

We define financial cost as the discounted sum of payments toward the loan plus the value of the loan, and substract to it the appraised or subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value - \frac{\text{I}(Recovered \: Pawn) \times Pawn \: Value}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a \hlgr{7\%} monthly interest rate. Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos conditional on recovering and conditional on not recovering the pawn. This cost is calculated for a time period of \hlgr{230 days} after loan origination, as \hlgr{51\%} of clients actually renew the loan one time and \hlgr{26\%} a second time. Of those who renew once \hlgr{36\%} lose the pawn, and of those that renew twice \hlgr{15\%} do. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.  Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 150\% and 250\% of the loan value. \hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.} We calculate an APR of \hl{23,000\% on average for the control group.}\footnote{The Annual Percentage Rate is calculated as the internal rate of return $i$ using the following formula \hl{XXX}.}

\section{Experiment} \label{Experiment}

\subsection{Treatment arms and randomization}

\noindent \textit{Selection of branches.} Starting \hlgr{August 6th} 2012, we implemented our experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes. In four of them the experiment ran for \hlgr{107} days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size. %Thus we eliminated \hl{the smallest} ones. 
Branches are more than \hl{5 km} apart from each other, and there is little substitution among them (only \hlgr{1\%} of consumers appear in more than one of our branches).

\vspace{.2in}
\noindent \textit{The monthly payment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one. It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days), and the gold pawn gets appraised in the same way by the same appraisers. The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement. Failure to pay these amount triggers a penalty fee of 2\% of this minimum amount due (in some of the treatment arms), which is added to the amount that the client needs to pay to recover their pawn. This penalty acts as a commitment device to pay now vs paying later. The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience. They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{As explained below we also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

\vspace{.2in}
\noindent \textit{Randomization.} Randomization was done at the branch-day level.  Each day the system chose which types of contracts were on offer that day in the branch, and therefore which contract the client signed. Branch personnel did not know which treatment would happen which day. They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied any given date, and that it could happen for instance that two consecutive dates had the same contract. They were also told that this way of operating was in effect in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months. Randomizing at the day level limits the problem of contamination arising from clients waiting for appraisal observing that other clients get different contracts than theirs. It also limits potential  manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen. Intra-branch correlation on the probability of default (ICC) is small, at \hlgr{0.08}, so we don't lose much power vis-a-vis individual level randomization.

\vspace{.2in}
\noindent \textit{Treatment Arms.} We have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.

\begin{enumerate}
    \item \textit{Status-quo} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly payment contract with a fee for late payment. 
    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly payment with fee contract, and the status quo contract.
    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee penalty. Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_. This is \underline{not} a legal document and cannot be used in courts. It is just a \textit{personal promise}. If I do not comply I would have broken my word.''. After signing, the promise was read to her by the appraiser.
    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the Promise-Forcing and the Status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them. The days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
\end{enumerate}

By comparing the \textit{Fee-Forcing} group vs \textit{Status-quo} group we estimate the causal effect of the commitment contract over the contract where the client can paying whenever they want in a 105 day period. On the other hand, having arms where clients could choose among these contracts allows us to study their demand for commitment. Note that a neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) and be subject to fees since she can always replicate the monthly payment profile herself under the status quo contract if she so desired. The status quo contract gives her extra flexibility to respond to income shocks for instance. However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value. This value would be traded off against the value of flexibility. This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done. Promises could have larger or smaller commitment value that a pecuniary fee, something that we test by comparing behavior in the \textit{Promise-Forcing}  vs \textit{Status-quo} arms.

Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has on each arm (rectangles). And for the choice arms, it displays in blue how many people actually chose the commitment contract.

%\subsection{Connection to the literature}
%Our study connects with two strands of the literature on microfinance. But also to a nascent one that uses RCTs to study to what extent people self-sort to treatments that have larger beneficial treatment effects for them. On the microfinance literature the first paper we could find that used an RCT to evaluate the causal effect of frequent payments in loans is \cite{Pande}. In a group lending rosca context, they note that most contracts involved frequent repayments --even weekly in many instances-- even when this increases transaction costs. They note that clients could benefit from ``the fiscal discipline afforded by the more rigid payments''. Frequency could provide a commitment device for clients, could foster a payment habit, or could generate more trust from social interactions among the group of borrowers. All these potential benefits apply in our context, except those relating to social interactions, as we work with individualized loans.

\subsection{More on implementation.}

We want to highlight two potential threats to the validity of our experiment. The first is that the client can chose to leave the branch after the appraiser values her pawn and tells her the contract terms, generating differential attrition across treatment arms. We anticipated this possibility and trained appraiser to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time. Empirically, attrition was not a problem. Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical. The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch). There is no evidence for selection across treatment arms for any of the admin or survey variables.

The second threat is clients' understanding of contract terms. We realized that we needed the terms to be understood in order for choice to be meaningful, and for the monthly payment commitment to have bite. We had two `check-points' to do this. First, two ITAM students were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms. One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or the psychological cost of breaking a promise) for failing to do so.  Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side). The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms. Students then asked clients to explain back the contract terms.

There was a second check point. Before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}. It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract. The appraised read it and asked the client to sign it as a proof of understating. The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3). Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms. The clients had to put their name in a slip of paper where they stated they promised to pay monthly.

We are fairly confident that the overwhelming majority of clients understood the contracts and made informed choices. As shows below, different contract terms did generate differential demand and differential behavior. Moreover, we can systematically predict demand based on consumer characteristics, beliefs and proxies for present biased preferences.

\section{The effect of forcing into fee-commitment} \label{fee-commitment}

\subsection{The effect of the fee-forcing contract on financial cost and pawn recovery} \label{TE_fee-forcing}

Now we answer our first question. Would clients benefit ---in terms of recovering their pawn and in terms of paying lower financing cost--- from having a monthly payment commitment contract \textit{forced} on them, vis-a-vis the status quo pay-when-you-want contract? We find they do. For each comparison, we separately estimate the regression equation (\ref{basic_reg}) below.

\begin{equation} \label{basic_reg}
    y_{ij} = \alpha + \beta T_{i} + \gamma X_{ij} + \epsilon_{ij}
\end{equation}

\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects, as well as dummies for the number of arms a client fell into and number of pieces pawned during the whole experiment\footnote{\hl{ISAAC: puedes incluir en appendix una tabla que muestre en que tratamientos cayeron todas la prendas durante el experimento? Y tambien un tab de cuantas personas empeniaron 1, 2, 3... piezas durante el experimento?}}. Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn. In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}

\vspace{.2in}
\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to using the appraised gold value of the pawned piece when the client loses it (not discounting makes virtually no difference). The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of \hlgr{11}\% in the fist definition and \hlgr{15\%} in the second one. That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.
